A Comparison of Graph Processing Systems

### 2020-09-28 documentation/paper/sections/introduction.tex
PushPull simplified

%!TEX root=../main.tex
\section{Introduction}
In recent years, graph processing has become increasingly important, both in academic and industrial environments \cite{Gemini}.
In many areas, such as machine learning and data mining, but also scientific computations \todo{Quellen}, problems can be modeled and solved with the help of graphs \cite{Polymer}.
Thus a new application domain called graph analytics was created.
Some business models are based on working with graphs, such as marketing analysis, advertising \todo{Quellen}, or even Google's search engine \cite{pagerank}.
In addition, the size of graphs has grown significantly in the last few years and will most likely continue to grow.
This makes the performance and memory efficiency of graph analysis applications more important than ever.
But also the parallelism and distribution of graph algorithms becomes more important with increasing graph sizes.
Parallelism may be important to exploit in order to finish the computations in an acceptable time frame.
It is especially important to utilize distributed computation when the RAM of a single node is insufficient for the task.

>>>>

%!TEX root=../main.tex
\section{Introduction}
In recent years, graph processing has become increasingly important, both in academic and industrial environments \cite{Gemini}.
In many areas, such as machine learning and data mining, but also scientific computations problems can be modeled and solved with the help of graphs \cite{Polymer}.
Thus a new application domain called graph analytics was created.
Some business models are based on working with graphs, such as marketing analysis, advertising or even Google's search engine \cite{pagerank}.
In addition, the size of graphs has grown significantly in the last few years and will most likely continue to grow.
This makes the performance and memory efficiency of graph analysis applications more important than ever.
But also the parallelism and distribution of graph algorithms becomes more important with increasing graph sizes.
Parallelism may be important to exploit in order to finish the computations in an acceptable time frame.
It is especially important to utilize distributed computation when the RAM of a single node is insufficient for the task.

### 2020-09-28 documentation/paper/sections/preliminiaries.tex
PushPull simplified

\subsection{Push and Pull Variants}
\todo{kompliziert}
Many parallel graph algorithms, including the three we consider here, are implemented by iterating over vertices \cite{tao}.
The vertex, to which the operator is applied, is called \emph{active}.
It's possible to iterate over edges and consider them as \emph{active}, but in the following, whithout loss of generality, we will use the term \emph{active vertex}.
This operator considers only a so called \emph{neighborhood} to the \emph{active} vertex.
To this \emph{neighborhood} belong only vertices, which are in the direct surrounding of the \emph{active} vertex.
This allows to parallelise the iteration relatively easy, caused by the locality of the operator.

In general such an operator can change the whole structure of the \emph{neighborhood}.
But in the following we assume, that an operator changes only \emph{labels} of vertices in the \emph{neighbourhood}.
\emph{Labels} of edges are also called \emph{weights}.
Often this operator can be implemented in two different ways, called \emph{push style} or \emph{pull style}.
A \emph{push-style} operator reads the \emph{label} of the \emph{active} vertex and updates the \emph{label} of its \emph{neighborhood}.
These operators are more efficient, if there are only a few \emph{active} vertices at the same time, or the \emph{neighborhoods} do not overlap, which can not be avoided in general.
In contrast the \emph{pull-style} operator reads all values of its \emph{neighborhood} and updates the value of the \emph{active} vertex.
\emph{Pull-style} operators need less synchronization in parallel implementations, because unlike \emph{push style} there is only one write and many read operations.
Thus locks can be avoided.
So these operators are more efficient, if there are many \emph{active} vertices at the same time.

>>>>

\subsection{Push and Pull Variants}
Many parallel graph algorithms, including the three we consider here, are implemented by iterating over vertices \cite{tao}.
To each of the vertices an operator is applied.
This operator reads and writes the labels of the active vertex and of the vertices in the direct surrounding, also called neighbourhood, of the active vertex.
It's also possible to iterate over edges, but in the following, whithout loss of generality, we will use the term active vertex.

Often this operator can be implemented in two different ways, called \emph{push style} or \emph{pull style}.
A \emph{push-style} operator reads the label of the active vertex and updates the label of its neighborhood.
These operators are more efficient, if there are only a few active vertices at the same time, or the neighborhoods do not overlap, which can not be avoided in general.
In contrast the \emph{pull-style} operator reads all values of its neighborhood and updates the value of the active vertex.
\emph{Pull-style} operators need less synchronization in parallel implementations, because unlike \emph{push style} there is only one write and many read operations.
Thus locks can be avoided.
So these operators are more efficient, if there are many active vertices at the same time.

### 2020-09-28 documentation/paper/sections/testingMethods.tex
PushPull simplified

\subsection{Methodology}
The testing methods cover the test environment, including hardware and the setup of the frameworks, the graphs used, followed by the algorithms utilized and our measuring procedures.

>>>>

\subsection{Methodology}
The methodology cover the test environment, including hardware and the setup of the frameworks, the graphs used, followed by the algorithms utilized and our measuring procedures.
